Data Munging

### 2020-09-22 scripts/dataMunge.Rmd
Resolving version conflicts in dgIndicatorAnalysis

The two data sets will be merged on the 'site id' fields.  The dissolved gas file contains data from sites in Alaska that are not present in the weights + lake area file.  Alaska sites are not an offical component of the NLA and will removed from this analysis.
``` {r}
# Will merge datasets on SITE_ID field.  Are all site.id values in dg present in wt.area?
dg %>% filter(!(site.id %in% wt.area$SITE_ID)) %>% distinct(site.id) # no.

@@

Three site visits contain only NA for temperature.  Four site visits contain only NA for do.  Two of the incidents include notes that sonde was forgotten or malfunctioning. Two of the three sites were revisited later in the study and temperature data were collected.  Lets assign data from the second site visit to the first visit when no temperature data were collected.  This leaves only NLA17_CA-10082, visit 1, without temperature data.  NLA17_ID-10084 has no DO data and was not resampled.  Data sheet comment "Probe not measuring LDO for all depths".

@@

No deep DO or temp at NLA17_MI-10073, visit 1 becuase no measurement taken at deepst recorded depth.  Replace with next shallowest measurement.

@@

No surface temp at NLA17_NE-10060, visit 1 becuase no measurement taken at shallowest depth (0m). Replace with next shallowest measurement (0.1m)

@@

No bottom temp or O2 at NLA17_NH-10063, visit 1 becuase no measurement taken at greatest depth (8m). Replace with next deeptest measurement (7.5m)

@@

No surface temp or O2 at NLA17_OR-10003, visit 1 becuase no measurement taken at shallowest depth (0m). Replace with next shallowest measurement (0.1m)

@@

No bottom temp or O2 at NLA17_SD-10057, visit 1 becuase no measurement taken at deepest depth (4m). Replace with next deepest measurement (3m)

@@

Only remainining missing values are observations where field crews noted sonde malfunctions.

>>>>

The two data sets will be merged on the 'site id' fields.  The dissolved gas file contains data from sites in Alaska that are not present in the weights + lake area file.  Alaska sites are not an official component of the NLA and will removed from this analysis.
``` {r}
# Will merge datasets on SITE_ID field.  Are all site.id values in dg present in wt.area?
dg %>% filter(!(site.id %in% wt.area$SITE_ID)) %>% distinct(site.id) # no.

@@

Three site visits contain only NA for temperature.  Four site visits contain only NA for DO.  Two of the incidents include notes that sonde was forgotten or malfunctioning. Two of the three sites were revisited later in the study and temperature data were collected.  Lets assign data from the second site visit to the first visit when no temperature data were collected.  This leaves only NLA17_CA-10082, visit 1, without temperature data.  NLA17_ID-10084 has no DO data and was not resampled.  Data sheet comment "Probe not measuring LDO for all depths".

@@

No deep DO or temp at NLA17_MI-10073, visit 1 because no measurement taken at deepest recorded depth.  Replace with next shallowest measurement.

@@

No surface temp at NLA17_NE-10060, visit 1 because no measurement taken at shallowest depth (0m). Replace with next shallowest measurement (0.1m)

@@

No bottom temp or O2 at NLA17_NH-10063, visit 1 because no measurement taken at greatest depth (8m). Replace with next deepest measurement (7.5m)

@@

No surface temp or O2 at NLA17_OR-10003, visit 1 because no measurement taken at shallowest depth (0m). Replace with next shallowest measurement (0.1m)

@@

No bottom temp or O2 at NLA17_SD-10057, visit 1 because no measurement taken at deepest depth (4m). Replace with next deepest measurement (3m)

@@

Only remaining missing values are observations where field crews noted sonde malfunctions.
